### 2015-04-20 paper.tex
Add Re table
Add tentative title

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions,
% and articles.
\begin{flushleft}
{\Large
\textbf\newline{Article Title - Submission to PLOS Journals}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include 
% titles, positions, or degrees).
\\
Name1 Surname\textsuperscript{1,\Yinyang},
Name2 Surname\textsuperscript{2,\Yinyang},
Name3 Surname\textsuperscript{2,\textcurrency a},
Name4 Surname\textsuperscript{2,\ddag},
Name5 Surname\textsuperscript{2,\ddag},
Name6 Surname\textsuperscript{2},
Name7 Surname\textsuperscript{3,*},
with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\bf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

@@

>>>>

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions,
% and articles.
\begin{flushleft}

{\Large \textbf\newline{Measurements on a 1:6 scale DOE Reference Model 2
cross-flow hydrokinetic turbine: Reynolds number dependence, near-wake dynamics,
and blade support strut drag}}
\newline
% Insert author names, affiliations and corresponding author email (do not include 
% titles, positions, or degrees).
\\
Name1 Surname\textsuperscript{1,\Yinyang},
Name2 Surname\textsuperscript{2,\Yinyang},
Name3 Surname\textsuperscript{2,\textcurrency a},
Name4 Surname\textsuperscript{2,\ddag},
Name5 Surname\textsuperscript{2,\ddag},
Name6 Surname\textsuperscript{2},
Name7 Surname\textsuperscript{3,*},
with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\bf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

@@

\begin{table}[ht]
\centering
\begin{tabular}{c|c|c}
Tow speed (m/s) & $Re_D$ & $Re_c$ at $\lambda = 3$ \\ 
\hline 
0.2 & $2.2 \times 10^5$ & $4.0 \times 10^4$ \\ 
0.4 & $4.3 \times 10^5$ & $8.0 \times 10^4$ \\ 
0.6 & $6.5 \times 10^5$ & $1.2 \times 10^5$ \\ 
0.8 & $8.6 \times 10^5$ & $1.6 \times 10^5$ \\ 
1.0 & $1.1 \times 10^6$ & $2.0 \times 10^5$ \\ 
1.2 & $1.3 \times 10^6$ & $2.4 \times 10^5$ \\ 
1.4 & $1.5 \times 10^6$ & $2.8 \times 10^5$ \\
\end{tabular} 
\caption{{\textbf Test Reynolds numbers.}Turbine diameter and approximate blade 
chord Reynolds numbers corresponding to tow speeds.} \label{tab:re}
\end{table}

\todo[inline]{Check which chord length was used to calculate $Re_c$, and
recalculate using $\lambda=3.1$.}
